Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-05-31 Doc/Vrst2013/vrst2013.tex
FIX: i7 CPU
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@588 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In the scenario presented in this paper, we focus on local influence of the capsule.
Nevertheless, it is possible to employ the actual model to demonstrate the global 
impact of the capsule and to further validate the accuracy of such a complete model w.r.t. experimental measures. 
Detailed description of such validation is however beyond the scope of this paper. 
In spite of this we would like to emphasize that we have already integrated the
capsule model with vascularized liver model described in~\cite{Peterlik2012}. 
Adding the capsule did not affect the
performance significantly: a visual refresh rate exceeding 25\,FPS was achieved on a
PC with CPU Intel CPU i7-2630QM running at 3.00 GHz.
This suggests that the proposed technique is compatible with real-time simulation of whole
organ while modeling the local properties accurately.

>>>>

In the scenario presented in this paper, we focus on local influence of the capsule.
Nevertheless, it is possible to employ the actual model to demonstrate the global 
impact of the capsule and to further validate the accuracy of such a complete model w.r.t. experimental measures. 
Detailed description of such validation is however beyond the scope of this paper. 
In spite of this we would like to emphasize that we have already integrated the
capsule model with vascularized liver model described in~\cite{Peterlik2012}. 
Adding the capsule did not affect the
performance significantly: a visual refresh rate exceeding 25\,FPS was achieved on a
PC with CPU Intel i7 running at 3.00 GHz.
This suggests that the proposed technique is compatible with real-time simulation of whole
organ while modeling the local properties accurately.
